---
title: "Formative Assessment 7"
author: "Ramilo, Zion John Yousef T."
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(car)
```
1. Provide an R or Python (with markdown) file for the independent samples t-test for Invisibility Cloak data set. 
- The file should have all the codes/and or explanations from Assumption 1 to 5 and computation.
- Present the results of the analysis by making a short report.
```{r}
df <- read_csv("DataSets/Invisibility Cloak.csv")
head(df)
```
Assumptions:

1. The dependent variable needs a continuous scale
2. The independent variable needs to have two independent groups with two levels.
3. The data should have independence of observations. More specifically,  there shouldn’t be the same participants in both groups.
4. The dependent variable should be normally or near-to-normally distributed for each group
5. There should be no extreme outliers.
6. The data must have homogeneity of variances.

(Assumption Check 1)
Check if the dependent variable is in a continuous scale.
Our dependent in the data set is the variable Mischief, where the values are in the interval form, where data like these are considered as continuous data.

(Assumption Check 2)
Check if the independent variable have independent groups with two levels.
The dataset has two distinct levels which are the groups with a cloak and the group without a cloak.

(Assumption Check 3)
Since there are distinct numbers for the participant variable then we can say that there are unique participants within the experiment and that there are no participants that participated on the other groups

(Assumption Check 4)
-> We can check normality using graphically and using the shapiro wilk test
```{r}
#Graphical
withoutCloakGroup <- df[df$Cloak == 0, ]

hist(withoutCloakGroup$Mischief, breaks = 5, probability = TRUE,
     main = "Distribution of Mischief (Cloak = 0)", xlab = "Mischief", ylab = "Density", col = "lightgreen")

```

```{r}
testForNormality_a <- shapiro.test(withoutCloakGroup$Mischief)
testForNormality_a
```

```{r}
withCloakGroup <- df[df$Cloak == 1, ]
hist(withCloakGroup$Mischief, breaks = 5, main = "Distribution of Mischief (Cloak = 1)", xlab = "Mischief", ylab = "Frequency", col = "lightpink")
```

```{r}
testForNormality_b <- shapiro.test(withCloakGroup$Mischief)
testForNormality_b
```
Lets test for overall dataset
```{r}
hist(df$Mischief, breaks = 10, main = "Distribution of Mischief", xlab = "Mischief", ylab = "Frequency", col = "lightblue")
```
```{r}
testForNormality_c <- shapiro.test(df$Mischief)
testForNormality_c
```
Let us say that our alpha or signifance level is at 0.05, 
Let H_0 = The data is normally distributed
Let H_a = The data is not normally distributed

Since our p values for all distributions for each groups and the combined groups are bigger than 0.05 then we fail to reject the null hypothesis therefore we can say that our data is normally distributed.

(Assumption Check 5)
Check if the data has extreme outliers.
```{r}
boxplot(df$Mischief, main = "Boxplot of Mischief", horizontal = TRUE)
```
It is worth noting that the t-test is robust for minor violations in normality. So we can have the data 0 within our dataset.

(Assumption Check 4)
Check if it passes the levene's test of homogeniety,
H_0 = the variances are homogeneous
H_a = the variances are not homogeneous
```{r}
df$Cloak <- as.factor(df$Cloak)
levene_Test<- leveneTest(df$Mischief ~ df$Cloak, data = df)
print(levene_Test)
```
Since our significant level is 0.05 and the p-value not beiiong able to be less than our signifance level indicates that we fail to reject our null hypothesis, meaning we can say that our data is homogeneous.

Since all assumptions are satisfied let us perform the t-test:
H_0 = There is no significant difference between the two groups
H_a = There is a significant difference between the two groups
```{r}
independentSamplesTTest <- t.test(df$Mischief ~ df$Cloak, data = df)
print(independentSamplesTTest)
```
Given by the p-value being greater than 0.05 we can say that we fail to reject our null hypothesis and therefore mean that there is no significant difference between the means of the two groups.

We have calculated a t value of a negative wherein this iimplies that group 0 must have a smaller mean than group 1, this mean tells us the expected times the group 0 conduct mischief is about 3.75 times whiles group 1 is about 5 times.





